Open Data, Open Source and Open Standards in chemistry: \\ The Blue Obelisk five years on

### 2011-06-04 paper.tex
Better AMBIT reference

A final example of second-generation Blue Obelisk software is the 
AMBIT2~\cite{WebAMBIT} software, a GUI that facilitates registration
of chemicals for the REACH EU directive on toxicity, and which is
based on the CDK.

>>>>

A final example of second-generation Blue Obelisk software is the 
AMBIT2~\cite{Jeliazkova2011} software, a GUI that facilitates registration
of chemicals for the REACH EU directive on toxicity, and which is
based on the CDK.
